\section{Coamenability of partial compact quantum groups}

Let $\mathscr{G}$ be a partial compact quantum group. 

%We will use throughout that if $\pi: P(\mathscr{G}) \rightarrow \End(V)$ is any $^*$-representation on a pre-Hilbert space (meaning $\langle v,\pi(a)w\rangle = \langle \pi(a^*)v,w\rangle$ for all $v,w\in V$), then $\pi$ extends to a $^*$-representation of $\CuG$ on the completion of $V$.

\begin{Def} A partial compact quantum group $\mathscr{G}$ will be called \emph{coamenable} if the natural projection map $\pi_{\red}:\CuG\twoheadrightarrow\CrG$ is an isomorphism.
\end{Def}

%Our aim is to give a characterisation of coamenability in terms of the representation theory of the fusion algebra, cf.~ \cite{Kye1} and references therein.

We will show that the usual characterisation of coamenability in terms of the counit representation holds. For this we need the following version of Fell's absorption principle. We will continue to use the notation introduced in the previous section.
% Definition \ref{DefTenProd} and the discussion preceding it.

\begin{Lem}\label{LemFell} Let $(\Hsp,\pi)$ be a non-degenerate $^*$-representation of $\CuG$. Then $\pi_{\red}\iboxtimes \pi$ factorizes over $\CrG$.
\end{Lem}

\begin{proof}  
  By Lemma \ref{lemma:partial-isometry}, the partial isometry
  $V_{\pi}$ restricts to a unitary \[U: \oplus_q
  (L^2(\mathscr{G})_q\otimes {}_q\Hsp ) \rightarrow \oplus_l ({}_l
  L^2(\mathscr{G})\otimes {}^l\Hsp),\]\[\Lambda(x)\otimes \xi \mapsto
  \Lambda(x_{(1)})\otimes \pi(x_{(2)})\xi,\quad x\in
  P(\mathscr{G}),\xi\in H,\] with inverse $\Lambda(x)\otimes \xi
  \mapsto \Lambda(x_{(1)})\otimes
  \pi(S(x_{(2)}))\xi$. %more info needed?
  Denote $\pi_{\red,q}$ for the restriction of $\pi_{\red}$ to
  $L^2(\mathscr{G})_q$. Then it is clear that $U$ intertwines
  $\oplus_q (\pi_{\red,q}\otimes 1)$ with $\pi_{\red}\boxtimes
  \pi$. As each $\pi_{\red,q}$ descends to $\CrG$, this proves the
  lemma.
\end{proof} 

Recall now from \cite{DCT1} the $^*$-representation 
\begin{align} \label{eq:weps}
  \weps: P(\mathscr{G}) \rightarrow \End(\C^{(I)}), \quad x\in
  \Gr{A}{k}{l}{m}{n}\mapsto \epsilon(x) e_{kl},
\end{align}
where $\epsilon$ denotes the counit of $P(\mathscr{G})$ and $\C^{(I)}$ the direct sum of $I$ copies of $\C$ with the natural pre-Hilbert space structure. We will denote its extension to a $^*$-representation $\CuG\rightarrow B(l^2(I))$ by the same symbol.

\begin{Lem}\label{LemUnit} Let $(\Hsp,\pi)$ be a non-degenerate $^*$-representation of $\CuG$. Then $\weps\iboxtimes \pi$ is unitarily equivalent to $\pi$.
\end{Lem} 
\begin{proof} The map \[U: \Hsp \rightarrow \oplus_k \left({}_kl^2(I)\otimes {}^k\Hsp\right),\quad \xi \mapsto \sum_k e_k\otimes \pi(\lambda_k)\xi\] is a unitary intertwiner.
\end{proof} 

\begin{Prop} The partial compact quantum group $\mathscr{G}$ is coamenable if and only if $\weps$ descends to a $^*$-representation of $\CrG$.
\end{Prop} 
\begin{proof} $\Rightarrow$ is clear. For $\Leftarrow$, note that $\Delta^u$ descends to a (non-unital) $^*$-homomorphism $\CrG\rightarrow M(\CrG\otimes \CuG)$ by Fell's absorption principle. Composing with $\weps\otimes \id$ and using Lemma \ref{LemUnit} with respect to a faithful representation of $\CuG$, we see that there exists a splitting $\CrG\rightarrow \CuG$ of $\pi_{\red}$, hence $\pi_{\red}$ is an isomorphism.
\end{proof}
 
We now pass to the character algebra of $\mathscr{G}$.
 
 \begin{Def} Let $\mathscr{X}$ be a unitary rcfd representation of a partial compact quantum group $\mathscr{G}$ on an $I$-bigraded Hilbert space $\Hsp$. The \emph{partial characters} of $\mathscr{X}$ are defined as \[\Gr{\chi}{}{X}{k}{l} = (\id\otimes \Tr)(\Gr{X}{k}{l}{k}{l}) = \sum_i(\Gr{X}{k}{l}{k}{l})_{ii} \in \Gr{P(\mathscr{G})}{k}{l}{k}{l},\] where $\Tr$ is the non-normalized trace on $B(\GrDA{\Hsp}{k}{l})$, and where $(\Gr{X}{k}{l}{k}{l})_{ij}$ denote matrix coefficients with respect to some fixed orthonormal basis. The \emph{total character} of $\mathscr{X}$ is the multiplier $\chi^X  =\underset{k,l}{\sum} \,\Gr{\chi}{}{X}{k}{l}\in M(P(\mathscr{G}))$.
 \end{Def}

%  For example, if $\mathscr{U}$ is the trivial representation of $\mathscr{G}$, then $\Gr{\chi}{}{U}{k}{l} = \delta_{k,l}\UnitC{k}{k}$, and $\chi^U = \sum_k \UnitC{k}{k}$.
 
%  Recall from \cite{DCT1} that $\smCirct$ denotes the tensor product of two representations of $\mathscr{G}$. 
 
% Denote by $\mathscr{U}$ 

%  \begin{proof} 
%  This follows from the definition of $\smCirct$, namely $\Gr{(X\Circt Y)}{k}{l}{m}{n} = \sum_{r,s} \left(\Gr{X}{k}{r}{m}{s}\right)_{12} \left(\Gr{Y}{r}{l}{s}{n}\right)_{13}$.
%  \end{proof}



 Denote by $\mathscr{U}$ the trivial representation of
 $\mathscr{G}$. Given an rcfd unitary representation $\mathscr{X}$ of
 $\mathscr{G}$ on an $I$-bigraded Hilbert space $\Hsp$, write $d^X_{kl} = \dim(\Gru{H}{k}{l})$. 
 \begin{Lem} \label{LemCharProps} 
   Let $\mathscr{X}$ and $\mathscr{Y}$ be unitary  rcfd representations of $\mathscr{G}$. Then
   \begin{align*}
     \Gr{\chi}{}{U}{k}{l} &= \delta_{k,l}\UnitC{k}{k}, &
     \Gr{\chi}{}{X\oplus Y}{k}{l} &=
     \Gr{\chi}{}{X}{k}{l} +      \Gr{\chi}{}{Y}{k}{l}, &
\Gr{\chi}{}{X\smCirct Y}{k}{m}&=\sum_{l}
     \Gr{\chi}{}{X}{k}{l}\Gr{\chi}{}{Y}{l}{m}, &
\Gr{\chi}{}{\hat X}{k}{l} &= (\Gr{\chi}{}{X}{l}{k})^{*}.
   \end{align*}
In total form, $\chi^{U}= \sum_{k} \UnitC{k}{k}$, $\chi^{X\oplus
  Y}=\chi^{X}+\chi^{Y}$,  $\chi^{X\Circt Y} =
     \chi^{X} \chi^{Y}$ and      $\chi^{\hat X} =
     (\chi^{X})^{*}$. Moreover, 
$\epsilon(\Gr{\chi}{}{X}{k}{l}) =d^{X}_{kl}$.
 \end{Lem}
 \begin{proof} 
This follows easily from the definitions, for example, one uses
\begin{align*}
  \Gr{(X\Circt Y)}{k}{l}{m}{n} &= \sum_{r,s}
   \left(\Gr{X}{k}{r}{m}{s}\right)_{12}
   \left(\Gr{Y}{r}{l}{s}{n}\right)_{13}, &
   \Gr{\hat X}{k}{l}{m}{n} &= (\id \otimes
   (-)^{tr})((\Gr{X}{l}{k}{n}{m})^{*})
\end{align*}
and $(\epsilon \otimes \id)(\Gr{X}{k}{l}{k}{l})=\id_{\Gru{H}{k}{l}}$,
where $\mathcal{H}$ denotes the Hilbert space
underlying $\mathscr{X}$.
\end{proof}

These relations show that the subspace $C\subseteq M(P(\mathscr{G}))$
spanned by the total characters of irreducible representations of
$\mathscr{G}$ is a $*$-algebra. We call it the \emph{character
  $*$-algebra} of $\mathscr{G}$.  



 Recall from \cite{DCT1} that a unitary rcfd representation of
 $\mathscr{G}$ is said to have \emph{finite hypersupport} if it is a
 \emph{finite} direct sum of irreducible unitary rcfd representations.
 The left hyperobject support of $\mathscr{X}$ is then the set of all
 $k$ such that $\GrDA{\Hsp}{k}{l}\neq \{0\}$ for some $l$. The right
 hyperobject support is defined similarly. Note that the left
 (resp. right) hyperobject support consists of hyperobject classes,
 where $k$ and $l$ define the same hyperobject class if
 $\UnitC{k}{l}\neq0$.

The unitary rcfd representations of $\mathscr{G}$ with finite
hypersupport form a partial
fusion  $C^{*}$-category $\Rep(\mathscr{G})$. We denote by
$\mathscr{C}$ the associated partial fusion $C^{*}$-algebra, whose
components $\Gru{C}{\alpha}{\beta}$ are the vector spaces generated by
the equivalence classes $[X]$ of irreducible unitary rcfd
representations of $\mathscr{G}$ with left and right hyperobject
support $\alpha$ and $\beta$, respectively, with multiplication and
involution given by 
\begin{align*}
  [X][Y] = \sum_{[Z]} \dim(\Hom(Z,X\Circt Y)) [Z] \quad \text{and} \quad [X]^{*} =[\hat{X}],
\end{align*}
respectively. Lemma \ref{LemCharProps} shows that the assignment $[X]
\mapsto \chi^{X}$ induces an isomorphism between the total algebra of
$\mathscr{C}$ and the character $*$-algebra $C$.


 We aim to show that each character $\chi^X$ is in fact a well-defined
 element in $M(\CuG)$ so that we can regard $C$ as a subalgebra of
 $M(C^{u}_{0}(\mathscr{G}))$ and of  $M(C^{r}_{0}(\mathscr{G}))$, respectively.

 \begin{Lem} \label{LemBoundDim} Let $\mathscr{X}$ be an rcfd unitary
   representation of $\mathscr{G}$ on an $I$-bigraded Hilbert space $\Hsp$ with finite hyperobject support. Then the matrix $D^X = (d^X_{kl})_{k,l}$ defines a bounded operator on $l^2(I)$. 
  \end{Lem}
  \begin{proof} We may assume that $\mathscr{X}$ is irreducible, say
    with left hyperobject support $\alpha$ and right hyperobject support
    $\beta$. Then we can find (a priori not necessarily bounded)
    morphisms \[R: \C^{(I)}\rightarrow \underset{k,l,m}{\oplus} \GrDA{H}{k}{m}\otimes
    \GrDA{H}{m}{l},\qquad \bar{R}: \C^{(I)} \rightarrow \underset{k,l,m}{\oplus}
    \GrDA{\bar{H}}{k}{m}\otimes \GrDA{\bar{H}}{m}{l},\] establishing a
    duality between $\underset{k,l}{\oplus} \GrDA{H}{k}{l}$ and
    $\underset{k,l}{\oplus}\GrDA{\bar{H}}{k}{l}$ inside the category of
    rcfd pre-Hilbert spaces. However, as $R^*R$ is a scalar multiple
    of the projection onto $\C^{(I_{\alpha})}$ by irreducibility, and
    similarly for $\bar{R}$, it follows that $R$ and $\bar{R}$ can be
    completed to bounded operators between the respective Hilbert
    space completions. It then follows from \cite[Lemma A.3.2]{DCY1}
    that 
    \begin{align} \label{eq:dim-estimate}
  \sup_k (\sum_l (d_{kl}^X+d_{lk}^X)) < \infty.    
    \end{align}
 By the Schur test,
    this implies that $D^X$ is bounded.
\end{proof} 


   
\begin{Lem} The sum $\chi^X  =\sum \Gr{\chi}{}{X}{k}{l}$ converges strictly to an element in $M(\CuG)$. 
\end{Lem} 
 
\begin{proof} It is sufficient to prove that the matrix of operators $\left(\pi\left(\Gr{\chi}{}{X}{k}{l}\right)\right)_{k,l}$ defines a bounded matrix of operators in some faithful $^*$-representation $\pi$ of $C^{u}_{0}(\mathscr{G})$. But as we have that each $\|\pi\left(\left(\Gr{X}{k}{l}{k}{l}\right)_{ij}\right)\|\leq 1$ by unitarity of $\mathscr{X}$, we have $\| \pi\left(\Gr{\chi}{}{X}{k}{l}\right)\| \leq d^X_{kl}$.  Hence boundedness follows from Lemma \ref{LemBoundDim}.
\end{proof} 

Denote by $\mathcal{C} \subseteq M(C_{0}^{r}(\mathscr{G}))$ the
$C^{*}$-algebra generated by the images of the $\chi^{X} \in
M(C_{0}^{r}(\mathscr{G}))$ for all rcfd unitary representations
$\mathscr{X}$ of $\mathscr{G}$ with finite hyperobject support, and by
 $\Irr(\mathscr{G})$ the equivalence classes of irreducible
unitary rcfd representations of $\mathscr{G}$.

The next result shows that the completion $\mathcal{C}$ of the
character $*$-algebra $C$ or, equivalently, of the total fusion
$*$-algebra of $\Rep(\mathscr{G})$,  depends only on
$\Rep(\mathscr{G})$.

\begin{Prop}
  There exists a unique faithful representation $\pi_{\mathcal{C}}$ of
  $\mathcal{C}$ on $l^{2}(\Irr(\mathscr{G}))$ such that for all
  $[X],[Y] \in \Irr(\mathscr{G})$,
  \begin{align} \label{eq:pi-c}
    \pi_{C}(\chi^{X})[Y] = \sum_{[Z] \in \Irr(\mathscr{G})}
    \dim(\Hom(Z,X\Circt Y))[Z].
  \end{align}
\end{Prop}
\begin{proof}
  For each hyperobject $\alpha$, choose an index $l(\alpha) \in
  \alpha$. Then the orthogonality relations \cite[Corollary
2.23]{DCT1} imply the existence of a unique isometry $\iota\colon
  l^{2}(\Irr(\mathscr{G})) \to L^{2}(\mathscr{G})$ such that
\begin{align*}
  [Y] &\mapsto \chi^{Y}_{l(\alpha)} \text{ for all } [Y] \in
  \Irr(\mathscr{G})_{\alpha},
\end{align*}
 and for all $[Y],\alpha$ as above and $[X] \in
\Irr(\mathscr{G})$,
\begin{align*}
  \chi^{X}\iota([Y]) = \chi^{X}\chi^{Y}_{l(\alpha)} = \chi^{X \Circt
    Y}_{l(\alpha)} =  \sum_{[Z \in \Irr(\mathscr{G})]}
  \dim(\Hom(Z,X\Circt Y)) \iota([Z]).
\end{align*}
Hence,   there   exists  a representation $\pi_{\mathcal{C}}$ such
satisfying \eqref{eq:pi-c}, and it remains to show that this
representation is faithful. 

Let $\chi = \chi^X$ with $[X] \in \Irr(\mathscr{G})$, $a\in
\Gr{P(\mathscr{G})}{k}{l}{m}{n}$ and $b\in
\Gr{P(\mathscr{G})}{r}{s}{p}{q}$. Then
\begin{align*}
  \langle
\Lambda(b),\chi \Lambda(a)\rangle = \langle \Lambda(
\UnitC{r}{r}),\chi \Lambda(a\sigma_{-i}(b^*))\rangle  =
 \langle \chi^{*} \Lambda(\chi^{\mathscr{U}}_{r})  |
 \Lambda(a\sigma_{-i}(b^*))\rangle.
\end{align*}
Denote by $\beta$ the hyperobject of $r$. Since the choice of the
assignment $\alpha \mapsto l(\alpha)$ in the first part of the proof
did not matter,  we may as well assume
$r=l(\beta)$ and find that $\Lambda(\chi^{\mathscr{U}}_{r})$ lies in
the image of $\iota$, and hence also $\chi^{*}
\Lambda(\chi^{\mathscr{U}}_{r})$. If $p$ denotes the projection onto
the image of $\iota$, we therefore find
\begin{align*}
  \langle
\Lambda(b) | \chi \Lambda(a)\rangle = 
 \langle p \Lambda(\chi^{\mathscr{U}}_{r})  | \chi
p \Lambda(a\sigma_{-i}(b^*))\rangle.
\end{align*}
By continuity, this holds for all elements $\chi \in \mathcal{C}$ and hence $\pi_{C}$ is faithful.
\end{proof}


By Lemma \ref{LemCharProps}, the $*$-representation $\weps \colon P(\mathscr{G})
\to l^{2}(\C^{(I)})$ defined in
\eqref{eq:weps}  acts on the character $*$-algebra $C$ by
\begin{align*}
  \weps(\chi^{X}) = \sum_{k,l} \epsilon(\Gr{\chi}{}{X}{k}{l})e_{kl} =
  \sum_{k,l} d^{X}_{kl} e_{kl} =D^{X}.
\end{align*}

%. In fact, since the representation on $L^2(\mathcal{C})_l$ is equivalent to the one on $L^2(\mathcal{C}_{l'})$ when $l$ and $l'$ belong to the same hyperobject, we see that $\mathcal{C}$ is determined completely by  itself.  


\begin{Def} We say $\mathscr{G}$ is \emph{dimension} coamenable %Fusion coamenable?
if the representation \[\tilde{\epsilon}: C \rightarrow B(l^2(I)), \quad \chi^X \mapsto D^X\] extends to a representation of $\mathcal{C}$.
\end{Def}

It is immediately clear that a coamenable partial compact quantum group is dimension coamenable. However, as we will see later, the converse is not true. This is in marked contrast with the case of quantum groups, where amenability of the fusion algebra (with respect to its \emph{scalar} dimension function) \emph{does} determine coamenability of the associated compact quantum group, cf. \cite[Theorem 4.5]{Kye1}.
 
 % Corollary: canonical partial quantum group constructed from a tensor C*-cat is always dimension coamenable, cf. Neshveyev-Tuset section 2.7

Recall now from \cite[Definition 1.23 and Section 4.1]{DCT1} the notion of \emph{canonical partial compact quantum group} associated to a \emph{partial fusion tensor C$^*$-category $\CatCC$}.

\begin{Prop} Let $\mathscr{G}_{\CatCC}$ be the canonical partial compact quantum group associated to an $\mathcal{I}$-partial fusion tensor C$^*$-category $\CatCC$. Then $\mathscr{G}_{\CatCC}$ is dimension coamenable.  
\end{Prop}% Ref to add to canonical partial compact quantum group
\begin{proof} 
  By construction, $\mathscr{G}_{\CatCC}$ is an $I$-partial compact quantum group, where $\Rep(\mathscr{G}_{\CatCC})$ can be canonically
  identified with $\CatCC$, and the set $I$ labels a maximal set
  $\{U_{k}\}$ of mutually non-isomorphic irreducible objects of
  $\CatCC$.  Under the Tannaka duality, an object $X$ of $\CatCC$
  corresponds to a corepresentation $\mathscr{X}$ of
  $\mathscr{G}_{\CatCC}$ on an $I$-bigraded Hilbert space $\Hsp$ with
  $\GrDA{\Hsp}{k}{l} = \Hom(U_k,X\otimes U_l)$. Now, $l^{2}(I) \cong
  l^{2}(\Irr(\mathscr{G}_{\CatCC}))$ via $k \mapsto [U_{k}]$ and
  \begin{align*}
    \pi_{C}(\chi^{X})[U_{l}] = \sum_{k} \dim(\Hom(U_{k}, X \Circt
    U_{l}))[U_{k}] = \sum_{m} d^{X}_{kl}[U_{l}]
  \end{align*}
  for all $k,l\in I$ and $[X] \in \Irr(\mathscr{G}_{\CatCC})$, showing
  that $\weps$ is equivalent to $\pi_{\mathcal{C}}$ and therefore
  extends to $\mathcal{C}$.
 \end{proof}
 
 In the next proposition, we consider the partial compact quantum groups associated to weighted reciprocal random walks, see \cite[Section 5]{DCT1}. 
 
 \begin{Prop} Consider the partial compact quantum group $\mathscr{G}(\Gamma)$ associated to a weighted reciprocal random walk $\Gamma = (\Gamma,i,w,\sgn)$. Then $\mathscr{G}(\Gamma)$ is dimension coamenable if and only if $\|\Gamma\| \leq 2$. 
 \end{Prop}% Ref to add to first article
 \begin{proof} As $\Rep(\mathscr{G}(\Gamma))$ is by construction a Temperley-Lieb category,  the character algebra $\mathscr{G}(\Gamma)$ is now the polynomial ring on one generator $\C\lbrack \chi_{1/2}\rbrack$, with $\chi_{1/2}$ the character of the generating object $u_{1/2}$ of $\Rep(\mathscr{G}(\Gamma))$. It has regular C$^*$-completion $C(\lbrack -2,2\rbrack)$, with $\chi_{1/2}$ corresponding to the identity function. 
 
Let now $\Gamma^{(0)}$ be the vertex set of $\Gamma$. Then $\Gamma^{(0)}$ is identified with the index set $I$ of $\mathscr{G}(\Gamma)$, and $D^{u_{1/2}}_{kl}$ is the number of arrows from $k$ to $l$. Hence we obtain that there exists a map $C(\lbrack -2,2\rbrack) \rightarrow B(l^2(\Gamma^{(0)}))$ with $\chi_{1/2}\mapsto D^{u_{1/2}}$ if and only if $\|D^{u_{1/2}}\| \leq  2$ if and only if $\|\Gamma\|\leq 2$.   
 \end{proof} 
 
 In particular, the partial compact quantum groups coming from
 dynamical quantum $SU(2)$ are dimension coamenable. However, as we
 will see in the next section, they are not coamenable.

% Coamenability in terms of invariant measure not considered yet.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "dynamical-SUq-file"
%%% End: 

