\documentclass[12pt]{article}

\usepackage{mathrsfs}

\usepackage{amssymb, amsthm, amsfonts, amsxtra, amsmath}
\usepackage{latexsym}
\usepackage{mathabx}
\usepackage[all]{xy}
\usepackage{graphics}
\usepackage{makeidx}
\usepackage{stmaryrd} % for llbracket/rrbracket

\usepackage{parskip} % paragraphs have no indents and vertical spacings inbetween
\makeatletter % need this to avoid the conflict between amsthm and parskip
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother


 \oddsidemargin -9mm\textwidth 17truecm


\topmargin -9mm \textheight 22truecm
\theoremstyle{change}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\ext}{\mathrm{e}}
\DeclareMathOperator{\can}{\mathrm{can}}
\DeclareMathOperator{\op}{\mathrm{op}}
\DeclareMathOperator{\fin}{\mathrm{f}}
\DeclareMathOperator{\Pol}{\mathrm{P}}
\DeclareMathOperator{\End}{\mathrm{End}}
\DeclareMathOperator{\Par}{\mathrm{Par}}
\DeclareMathOperator{\reg}{\mathrm{reg}}
\DeclareMathOperator{\sgn}{\mathrm{sgn}}
\DeclareMathOperator{\Zz}{\mathrm{Z}}
\DeclareMathOperator{\Ran}{\mathrm{Ran}}
\DeclareMathOperator{\hol}{\mathrm{hol}}
\DeclareMathOperator{\Ind}{\mathrm{Ind}}
\DeclareMathOperator{\Ker}{\mathrm{Ker}}
\DeclareMathOperator{\Char}{\mathrm{Char}}
\DeclareMathOperator{\dyn}{\mathrm{dyn}}
\DeclareMathOperator{\Spec}{\mathrm{Spec}}

\newcommand{\nc}{\R}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\h}{\mathfrak{h}}
\newcommand{\kk}{\mathfrak{k}}
\newcommand{\ttt}{\mathfrak{t}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\n}{\mathfrak{n}}
\newcommand{\llll}{\mathfrak{l}}
\newcommand{\uu}{\mathfrak{u}}
\newcommand{\bb}{\mathfrak{b}}
\newcommand{\q}{\mathfrak{q}}
\newcommand{\su}{\mathfrak{su}}
\newcommand{\ssl}{\mathfrak{sl}}
\newcommand{\so}{\mathfrak{so}}
\newcommand{\spp}{\mathfrak{sp}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\e}{\mathfrak{e}}
\newcommand{\s}{\mathfrak{s}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\X}{\mathbb{X}}
\newcommand{\Y}{\mathbb{Y}}
\newcommand{\Ss}{\mathbb{S}}
\newcommand{\ZZ}{\mathscr{Z}}
\newcommand{\ad}{\mathrm{ad}}
\newcommand{\Hsp}{\mathscr{H}}
\newcommand{\qn}[2]{\lbrack #1 \rbrack_{#2}}
\newcommand{\fqn}[2]{\lbrack #1 \rbrack_{#2}!}
\newcommand{\bqn}[3]{\left\lbrack \begin{array}{c} \!#1\! \\ \!#2\! \end{array}\right\rbrack_{#3}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\RR}{\mathcal{R}}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\res}{\mathrm{res}}
\newcommand{\cop}{\mathrm{cop}}
\newcommand{\opp}{\mathrm{op}}
\newcommand{\Rm}{\mathcal{R}}
\newcommand{\wt}{\mathrm{wt}}
%\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\CatC}{\mathcal{C}}
\newcommand{\CatD}{\mathcal{D}}
\newcommand{\Corr}{\mathrm{Corr}}
\newcommand{\Hilb}{\mathrm{Hilb}}
\newcommand{\Star}[2]{{}_{#1}\!*_{#2}}
\newcommand{\vot}{\bar{\otimes}}
\newcommand{\A}{\mathcal{B}}
\newcommand{\Aa}{\mathscr{B}}
\newcommand{\Mor}{\mathrm{Mor}}
\newcommand{\alg}{\mathrm{alg}}
\newcommand{\Gg}{\mathscr{G}}
\newcommand{\ev}{\mathrm{ev}}
\newcommand{\Rtimes}{\underset{\R}{\times}}
\newcommand{\Rb}{\R^{\bullet}}
\newcommand{\vtimes}{\bar{\otimes}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\Tt}{\mathscr{T}}
\newcommand{\Gr}[5]{\;{}^{\;#2}_{#4}#1_{#5}^{#3}}%TODO: better typesetting
\newcommand{\Grl}[3]{\;{}^{\;#2}_{#3}#1}%TODO: better typesetting
\newcommand{\Gru}[3]{\;{}^{\;#2}#1^{#3}}
\newcommand{\Grd}[3]{\;{}_{\;#2}#1_{#3}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Ff}{\Fun_{\fin}}
%\newcommand{\fin}{\mathrm{fin}}
\newcommand{\iitimes}{\underset{I}{\otimes}}
\newcommand{\itimes}{\underset{I^2}{\otimes}}
\newcommand{\osum}[1]{\underset{#1}{\sum}^{\oplus}}
\newcommand{\wDelta}{\widetilde{\Delta}}


\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lem}[Theorem]{Lemma}
\newtheorem{Prop}[Theorem]{Proposition}
\newtheorem{Cor}[Theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{Def}[Theorem]{Definition}
\newtheorem{Rem}[Theorem]{Remark}
\newtheorem{Exa}[Theorem]{Example}
\newtheorem{Not}[Theorem]{Notation}
\newtheorem{Que}[Theorem]{Question}
\newtheorem{Con}[Theorem]{Conjecture}

\date{}


\numberwithin{equation}{section}

\begin{document}
\title{Generalized face algebras{\scriptsize, ergodic actions of compact quantum groups and dynamical quantum $SU(2)$}}

\author{Kenny De Commer\thanks{Department of Mathematics, University of Cergy-Pontoise, UMR CNRS 8088, F-95000 Cergy-Pontoise, France, email: {\tt Kenny.De-Commer@u-cergy.fr}}
\and Thomas Timmermann\thanks{University of M\"{u}nster}}

\maketitle


\begin{abstract}
\noindent We present a generalized definition of Hayashi's compact face algebras which allows for an infinite-dimensional base algebra. {\scriptsize As the main source of examples, we show how any quantum homogeneous space of a compact quantum group leads to such a generalized compact face algebra. In particular, we show how the construction applied to a non-standard Podle\'{s} sphere, seen as a quantum homogeneous space for quantum $SU(2)$, leads to an implementation of the dynamical quantum $SU(2)$-group as a generalized compact face algebra.}
\end{abstract}


%\begin{abstract}
%\end{abstract}

%\emph{Keywords}:

%AMS 2010 \emph{Mathematics subject classification}:


%17B37: Quantum groups, quantized enveloping algebras
%20G42: quantized function algebras
%46L65: Functional analysis, deformations, quantizations
%81R50: Quantum groups and related algebraic methods
%16T05: Hopf algebras and their applications
%16T10: Bialgebras
%16T15: Coalgebras and comodules; corings
%46L08  $C^*$-modules



% TODO: clarify link with weak Hopf algebras (Van Daele and Wang) and weak bialgebras (Bohm et al)
\section{Compact Hopf Face Algebras}

\subsection{Preliminaries}

If $I$ is a set, we write $\Fun_{\fin}(I)$ for the algebra of \emph{finitely supported} $\C$-valued functions on $I$, and $\Fun(I)$ for the algebra of \emph{all} $\C$-valued functions on $I$. By $I^n$ we denote the $n$-fold Cartesian product of $I$ with itself. We will always suppose that $I$ is at most countable.

By an algebra, we will understand an associative algebra $A$ over $\C$ which does not necessarily contain a unit, but which has local units in the sense that for each finite set of elements $a_i\in A$, there exists $e\in A$ such that $a_ie=a_i=ea_i$ for all $i$. Then $A$ embeds into its multiplier algebra $M(A)$, which is the subalgebra of $\End(A)\oplus \End(A)^{\op}$ consisting of linear endomorphisms $m = (L_m,R_m^{\op})$ for which $b(L_ma) = (R_mb)a$ for all $a,b\in A$. The embedding is by means of the map $a \mapsto (L_a,R_a^{\op})$ where $L_a$ and $R_a$ denote respectively left and right multiplication with $a$. In the following, we simply identify $A$ as a subalgebra of $M(A)$. As an example, we have that $\Fun_{\fin}(I)$ is an algebra with $M(\Fun_{\fin}(I)) = \Fun(I)$.

If $A$ and $B$ are algebras, a homomorphism $f:A\rightarrow M(B)$ is called \emph{non-degenerate} if $f(A)B = B = Bf(A)$. In this case, $f$ extends uniquely to a unital homomorphism $M(A)\rightarrow M(B)$, which we will denote by the same symbol. We will call non-degenerate homomorphisms simply \emph{morphisms}. A morphism $f$ such that $f(A)=B$ will be called a \emph{strong} morphism. Note that if $f$ is a morphism, we can find local units for $B$ in $f(A)\subseteq M(B)$.

% TODO: specify what $^*$-structure is, give standard *-structure on $\Fun(I)$
% TODO: better terminology?
\begin{Def} Let $I$ be a set. An algebra $A$ is called an $I$-algebra if it comes equipped with a morphism \[\Fun_{\fin}(I) \rightarrow M(A).\] It is called a \emph{strong} $I$-algebra if this morphism is strong.
\end{Def}

% TODO: take care of bad typesetting
Note that by non-degeneracy, we obtain a map $\Fun(I)\rightarrow M(A)$. This implies that for any $k\in I$, we have idempotent mutually orthogonal elements $e_k$ in $M(A)$ corresponding to the image of the functions \[m \mapsto \delta_{k,m}.\] Hence, again by non-degeneracy, $A$ has a $I^{2}$-grading \[ A = \osum{k,l}\Gru{A}{k}{l}, \qquad  \Gru{A}{k}{l} =  e_kAe_l.\] If $A$ is a strong $I$-algebra, the $\Gru{A}{k}{k}$ will be unital with unit $e_k$, and the $\Gru{A}{k}{l}$ are (unital) $\Gru{A}{k}{k}$-$\Gru{A}{l}{l}$-bimodules.

Similarly, if $A$ is an $I^2$-algebra, we have for any $k\in I$ elements $\lambda_k$ and $\rho_k$ in $M(A)$ corresponding respectively to the image of the functions \[(m,n) \mapsto \delta_{k,m},\qquad (m,n)\mapsto \delta_{k,n}.\] This gives a $I^4$-grading on $A$ by putting \[\Gr{A}{k}{l}{m}{n} = \lambda_k\rho_mA\lambda_l\rho_n.\] It is then clear that when $m,n\in I$, the symbol $\Grd{A}{m}{n}$ will denote $\osum{m,n} \Gr{A}{k}{l}{m}{n}$, etc.

\begin{Def} If $A$ is an $I^2$-algebra, we will say $A$ is \emph{faithful} if $\lambda_k\neq 0$ for all $k$, and similarly $\rho_m\neq 0$ for all $m$.\end{Def}

\begin{Def} Let $A,B$ be two $I^2$-algebras. We define $A\itimes B$ to be the subalgebra \[\osum{r,s} \Grd{A}{r}{s}\otimes \Gru{B}{r}{s} \subseteq A\otimes B,\] seen as an $I^2$-algebra by means of the map $\delta_{(k,l)}\mapsto \lambda_k\itimes \rho_l$, where the latter tensor is the restriction to $A\itimes B$ of the multiplier $\lambda_k\otimes \rho_l$ of $A\otimes B$.
\end{Def}

\begin{Rem} Note that $A\itimes B$ will indeed again have local units and be faithful. The $\itimes$-product then clearly defines an associative product on $I^2$-algebras.
\end{Rem}

\begin{Rem} One has for $A\itimes B$ also the multiplier $\rho_p\itimes \lambda_p = \rho_p\itimes 1 = 1\itimes \lambda_p$, which acts again by restriction of the corresponding multipliers on $A\otimes B$.
\end{Rem}

\begin{Rem}\label{RemCut} If $A$ is an algebra, we can endow $M(A)$ with the topology for which $m_{\alpha}\rightarrow m$ if for any $a\in A$, we have eventually that $m_{\alpha}a=ma$ and $am_{\alpha}=am$. If then $A$ and $B$ are $I^2$-algebras, we can write $A\itimes B = E(A\otimes B)E$ where $E \in M(A\otimes B)$ is the idempotent multiplier $\sum_{p}\rho_p\otimes \lambda_p$, the sum obviously converging (over the net of all finite subsets of $I$) in the above topology.
\end{Rem}


\begin{Def} Let $A,B$ be two $I$-algebras. An $I$-morphism from $A$ to $B$ will mean a morphism $f:A\rightarrow M(B)$ intertwining the $\Fun_{\fin}(I)$-morphisms.
\end{Def}

Clearly, one can form tensor products $f\itimes g$ of $I^2$-morphisms, giving a morphism between $\itimes$-tensor products. The non-degeneracy of $f\itimes g$ can again be shown by a local unit argument.

\subsection{Generalized Hopf face algebras}

\begin{Def} Let $I$ be a set, and $A$ an $I^2$-algebra. By an \emph{$I^2$-coproduct} on $A$, we will mean a coassociative $I^2$-morphism $\Delta:A\rightarrow M(A\itimes A)$, i.e. \[(\Delta\itimes \id)\Delta = (\id\itimes \Delta)\Delta.\]
\end{Def}

\begin{Rem}\label{RemMult} As $\Delta$ is an $I^2$-morphism, we have $\Delta(\lambda_k\rho_l) =\lambda_k\itimes \rho_l$. Hence if $A$ is a \emph{strong} $I^2$-algebra, this implies that for any $p\in I$ we have \[(\rho_p\itimes 1)\Delta(A) = (1\itimes \lambda_p)\Delta(A) \subseteq A\itimes A \qquad \textrm{and}\qquad \Delta(A)(\rho_p\itimes 1)= \Delta(A)(1\itimes \lambda_p) \subseteq A\itimes A.\]
\end{Rem}

% TODO: elaborate
\begin{Rem} If $A$ is a strong $I^2$-algebra, we have an inclusion $M(A\itimes A)\rightarrow M(A\otimes A)$ by means of \[m\mapsto \sum_{k,l,p} m(\lambda_k\rho_p\itimes \lambda_p\rho_l) = \sum_{k,l,p} (\lambda_k\rho_p\itimes \lambda_p\rho_l)m.\] Hence an $I^2$-coproduct $\Delta$ then `co-extends' to an algebra homomorphism \[\wDelta: A\rightarrow M(A\otimes A)\] such that \[\wDelta(A)(A\otimes A) = E(A\otimes A),\qquad (A\otimes A)\wDelta(A) = (A\otimes A)E,\] where $E$ again denotes the element $\sum_{p}\rho_p\otimes \lambda_p$. This $\wDelta$ then extends (uniquely) to an algebra homomorphism $M(A)\rightarrow M(A\otimes A)$ such that $\wDelta(1) = E$, cf. [Van Daele and Wang; B\"{o}hm et al]. By definition, we have \[\wDelta(a)(\lambda_k\rho_m\otimes \lambda_l\rho_n) = \delta_{m,l}\Delta(a)(\lambda_k\rho_m\itimes \lambda_m\rho_n), \qquad (\lambda_k\rho_m\otimes \lambda_l\rho_n) \wDelta(a)= \delta_{m,l}(\lambda_k\rho_m\itimes \lambda_m\rho_n)\Delta(a)\] for all $a\in A$ and all $k,l,m,n\in I$. This implies that \[\Delta(a)(1\itimes \lambda_l\rho_n) = \wDelta(a)(1\otimes \lambda_l\rho_n)\] for all $a\in A$ and $l,n\in I$, and similarly for other expressions of this kind. Hence we see that \[\wDelta(A)(1\otimes A)\cup \wDelta(A)(A\otimes 1)\cup (A\otimes 1)\wDelta(A)\cup (1\otimes A)\wDelta(A)\subseteq A\otimes A.\]
\end{Rem}

\begin{Def} A \emph{generalized face algebra over $I$} consists of a strong $I^2$-algebra $A$ together with an $I^2$-coproduct and a functional $\varepsilon:A\rightarrow \C$ such that \[(\id\otimes \varepsilon)((a\otimes 1)\wDelta(b)(c\otimes 1)) = abc = (\varepsilon\otimes \id)((1\otimes a)\wDelta(b)(1\otimes c))\] for all $a,b,c\in A$, and \begin{equation}\label{EqBoh}(\varepsilon\otimes \varepsilon)((a\otimes 1)\wDelta(b)(1\otimes c)) = \varepsilon(abc) = (\varepsilon\otimes \varepsilon)((1\otimes a)\wDelta(b)(c\otimes 1))\end{equation} for all $a,b,c\in A$.% Is Hayashi axiom sufficient, or should indeed the Bohm axiom be taken?
\end{Def}




%The following lemma is immediate.

%\begin{Lem} We have $\varepsilon(\Gr{A}{k}{l}{m}{n}) = \delta_{k,m}\delta_{n,l}\C$.\end{Lem}

We will use the Sweedler notation for the coproduct $\wDelta$ from now on.

\begin{Def} Let $I$ be a set. A \emph{generalized Hopf face algebra over $I$} is a generalized face algebra $(A,\Delta)$ admitting an invertible anti-homomorphism $S:A \rightarrow A$ such that $S(\lambda_k\rho_m) = \lambda_m\rho_k$ for all $k,m\in I$ and such that \[S(a_{(1)})a_{(2)}b = \sum_n\varepsilon(a\lambda_n)\rho_nb, \qquad ba_{(1)}S(a_{(2)}) = \sum_k\varepsilon(\rho_ka)b\lambda_k\] for all $a,b\in A$.
\end{Def}

\begin{Rem} Imposing the invertibility of $S$ corresponds to the \emph{regularity} condition in the case of multiplier Hopf algebras, see [VDae]. We refrain from seeing it as a separate condition as it will be satisfied automatically in the examples under consideration.
\end{Rem}

\begin{Rem} If $(A,\Delta)$ is a generalized Hopf face algebra, then also $(A^{\op},\Delta)$ and $(A,\Delta^{\op})$ are (the embeddings of $\Ff(I^2)$ being unchanged), with the same counit maps and their antipodes being given by $S^{-1}$.

\end{Rem}

% To prove: $S$ is anti-multiplicative

\begin{Lem} Let $(A,\Delta)$ be a generalized Hopf face algebra over $I$. Then $\varepsilon(\lambda_k\rho_m)=\delta_{k,m}$.
\end{Lem}
\begin{proof} As $\wDelta(\lambda_k\rho_m) = \sum_p \lambda_k\rho_p\otimes \lambda_p\rho_m$, we find that $\lambda_k\rho_m = \sum_p  \varepsilon(\lambda_p\rho_m)\lambda_k\rho_p$. Hence if $p\neq m$, we have $\varepsilon(\lambda_p\rho_m)\lambda_k\rho_p=0$. Applying $S$, we see that $\varepsilon(\lambda_p\rho_m)=0$.

We conclude that $\lambda_k\rho_m = \varepsilon(\lambda_m\rho_m)\lambda_k\rho_m$. As $\rho_m \neq 0$, varying $k$ shows that necessarily $\varepsilon(\lambda_m\rho_m)=1$.
\end{proof}


\begin{Lem} For all $a\in A$ and $m,n\in I$, we have $\varepsilon(a\lambda_k) = \varepsilon(a\rho_k)$ and $\varepsilon(\lambda_la)=\varepsilon(\rho_la)$.
\end{Lem}
\begin{proof} From the axiom \ref{EqBoh}, it follows that $\sum_p \varepsilon(a\rho_p)\varepsilon(\lambda_pb)= \varepsilon(ab)$ for all $a,b\in A$. Taking $b = \lambda_k\rho_m$, we find that $\varepsilon(a\rho_k)\varepsilon(\lambda_k\rho_m) = \varepsilon(a\lambda_k\rho_m)$. Taking $m=k$ and applying the previous lemma, we find $\varepsilon(a\rho_k)=\varepsilon(a\lambda_k\rho_k)$, implying one half of the lemma. The other half is proven similarly.
\end{proof}

\begin{Def} Define \[V: \osum{n} A_n\otimes {}_{n}A \rightarrow \osum{r} {}_rA\otimes {}^rA\] by the formula \[a\otimes b\rightarrow \wDelta(a)(1\otimes b).\]
\end{Def}

\begin{Lem}\label{LemUni} The map $V$ is an isomorphism.
\end{Lem}
\begin{proof} As $\wDelta(A)(A\otimes A)\subseteq E(A\otimes A)$ with $E = \sum_p \rho_p\otimes \lambda_p$, it is clear that $V$ has the proper range. Define \[\widetilde{V}:  \osum{r} {}_rA\otimes {}^rA\rightarrow\osum{n} A_n\otimes {}_{n}A\] by means of the formula \[a\otimes b \mapsto a_{(1)}\otimes S(a_{(2)})b = a_{(1)}\otimes S(S^{-1}(b)a_{(2)}).\]

By the defining property of $S$, we find that for all $a,b,c\in A$, we have \[(c\otimes 1)\cdot (\widetilde{V}V)(a\otimes b) = \sum_p ca_{(1)}\varepsilon(a_{(2)}\lambda_p)\otimes \rho_pb.\] By the previous lemma, this equals $\sum_p ca_{(1)}\varepsilon(a_{(2)}\rho_p)\otimes \rho_pb$. But as $a\otimes b = \sum_p a\rho_p\otimes \rho_pb$ by assumption, we obtain that \[(c\otimes 1)\cdot (\widetilde{V}V)(a\otimes b) = ca_{(1)}\varepsilon(a_{(2)})\otimes b = ca\otimes b,\] proving that $\widetilde{V}V(a\otimes b) = a\otimes b$.

The identity $V\widetilde{V} = \id$ is proven similarly.
\end{proof}

\begin{Cor} Define \[W: \osum{n} {}_n A \otimes {}^nA  \rightarrow \osum{r} \; {}^rA\otimes A^r\] by the formula \[a\otimes b \rightarrow S^{-1}(b_{(1)})a\otimes d_{(2)} = S^{-1}(S(a)b_{(1)})\otimes b_{(2)}.\] Then $W$ is invertible, its inverse being given as \[W^{-1}(a\otimes b) = \wDelta(b)(a\otimes 1).\]
\end{Cor}

\begin{proof} Apply the previous Lemma to $(A,\Delta^{\op})$.
\end{proof}

\subsection{Invariant functionals}

\begin{Def} Let $I$ be a set. An \emph{invariant functional} for a generalized Hopf face algebra $(A,\Delta)$ over $I$ is a functional $\varphi:A \rightarrow \C$ such that for all $a\in A$, we have the identity of multipliers \[(\id\otimes \varphi)\wDelta(a) = \sum_p \varphi(\lambda_p a)\lambda_p,\qquad (\varphi\otimes \id)\wDelta(a) = \sum_p\varphi(a\rho_p)\rho_p.\] We say that $\varphi$ is normalized if $\varphi(\lambda_k\rho_l)=1$ for all $k,l\in I$ with $\lambda_k\rho_l\neq 0$.
\end{Def}

%\begin{Lem} We have $\varphi(\Gr{A}{k}{l}{m}{n}) = \delta_{k,l}\delta_{m,n}\C$.\end{Lem}

% TODO: make connection with weak multiplier Hopf algebras

\begin{Lem} An invariant normalized functional $\varphi$ is faithful, i.e. $\varphi(ab)=0$ for all $b$ implies $b=0$, and $\varphi(ab)=0$ for all $a$ implies $b=0$.
\end{Lem}

\begin{proof} We follow ad verbatim the proof of Proposition 3.4 in [VDae, Algebraic framework]: if $\varphi(ba)=0$ for all $a$, we arrive at the conclusion that for all $d\in A$ and all functionals $\omega$ on $A$, the element $p = (\omega\otimes \id)((d\otimes 1)\wDelta(a))$ satisfies $(\id\otimes \varphi)((1\otimes c)\wDelta(p)) = 0$. Continuing as in that proof, we obtain from the antipode trick that $\sum_n \varphi(cS(q)\rho_n)\varepsilon(p\lambda_n)=0$. Choosing now for $c$ and $q$ local units of the form $\lambda_k\rho_l$, the normalization condition on $\varphi$ gives that $\varepsilon(p\lambda_n)=0$ for all $n$, hence $\varepsilon(p)=0$. This implies $\omega(da)=0$. As $\omega$ and $d$ were arbitrary, it follows that $a=0$.

The other case follows similarly, considering the opposite algebra.
\end{proof}

% This part is necessary to put into Enock framework, but might possibly be skipped if we only want an operator algebra implementation of dynamical quantum SU(2), as then one has enough with the multiplicative unitaries
Our next aim is to prove that a normalized invariant functional is modular, that is, there exists an automorphism $\sigma: A\rightarrow A$ such that for all $a,b\in A$, we have \[\varphi(ba) = \varphi(a\sigma(b)).\]

\begin{Lem} Let $\varphi$ be a normalized invariant functional. For all $a\in A$ and $k,m\in I$, we have \[\varphi(a\lambda_k) = \varphi(\lambda_ka),\qquad \varphi(a\rho_m) = \varphi(\rho_ma).\]
\end{Lem}

\begin{proof}

\end{proof}


\subsection{Generalized compact Hopf face algebras}


A non-degenerate algebra $A$ is called a $^*$-algebra if it comes equipped with an anti-linear involutive anti-homomorphism $A\rightarrow A, a\mapsto a^*$. In this case, $M(A)$ becomes a $^*$-algebra in a natural way. For example, we always consider $\Fun_{\fin}(I)$ as a $^*$-algebra by the ordinary complex conjugation of functions, $f^*(k) = \overline{f(k)}$.




\begin{Def} A couple $(A,\Delta)$ consisting of a generalized Hopf face $^*$-algebra with an invertible antipode invariant normalized functional $\varphi$ is called a \emph{generalized compact face algebra}.
\end{Def}

One proves that a generalized Hopf face $^*$-algebra has $S(S(x)^*)^*=x$ for all $x$, so $S$ is automatically invertible. It then follows by symmetry that also the maps \[(W^{k,t}_{m,n,u,v})^*: \oplus_l \Gr{A}{k}{l}{m}{n} \otimes \Gr{A}{l}{t}{u}{v} \rightarrow \oplus_r \Gr{A}{k}{t}{m}{r}\otimes \Gr{A}{n}{r}{u}{v}\] defined by the formula \[a\otimes b\rightarrow \Delta(b)(a\otimes 1)\] are unitaries, with inverse map $a\otimes b\mapsto S^{-1}(b_{(1)})a\otimes b_{(2)}$.

\begin{Lem}\label{LemUni} Let $(A,\Delta)$ be a generalized compact face algebra. Then each $V^{k,l,s,t}_{m,v}$ is a unitary, and similarly for the $W^{k,t}_{m,n,u,v}$.
\end{Lem}

\begin{proof} It is immediately checked that $V^{k,l,s,t}_{m,v}$ is isometric.
\end{proof}

Let us write $\mathscr{L}^2(A,\varphi)$ for the completion of $A$ with respect to the inner product $\langle a,b\rangle = \varphi(a^*b)$. The canonical inclusion of $A$ into $\mathscr{L}^2(A)$ will be denoted $\Lambda$.

\begin{Lem} Assume $(A,\Delta)$ is a generalized compact face algebra. The representation of $A$ by left multiplication on itself extends to a representation by bounded operators on the completion $\mathscr{L}^2(A,\varphi)$.
\end{Lem}

\begin{proof} Denote $\omega_{\xi,\eta}(x) = \langle \xi,x\eta\rangle$ for $\xi,\eta$ vectors and $x$ a bounded operator. Then a straightforward computation shows that \[(\omega_{\Lambda(a),\Lambda(b)}\otimes \id)(V) = \varphi(a^*b_{(1)})b_{(2)}\] as a left multiplication operator. As $(A\otimes 1)\Delta(A) = (A\otimes A)\Delta(1)$ by Lemma \ref{LemUni} (applied to the opposite algebra), it follows by normalization of $\varphi$ that each element of $A$ can be represented in the form $(\omega_{\Lambda(a),\Lambda(b)}\otimes \id)(V)$, and hence extends to a bounded operator on $\mathscr{L}^2(A,\varphi)$.
\end{proof}

In the following, we will abbreviate $\mathscr{L}^2(A)$ by $L^2A$.

Let $(A,\Delta)$ be a generalized compact face algebra. Denote the von Neumann algebraic completion of $A\subseteq B(L^2A)$ by $M$. Denote $L^2A\iitimes L^2A = E(L^2A\otimes L^2A)$, where $E = \sum_p \rho_p\otimes \lambda_p$ is extended to a bounded operator (in fact, a self-adjoint projection). Finally, denote $M\itimes M = E(M\otimes M)E$. Then $M\itimes M$ is the von Neumann algebraic completion of $A\itimes A$.

Extend now the $V^{k,l,s,t}_{m,v}$ to unitaries \[V: \oplus_p L^2(A_p)\otimes L^2({}_pA) \rightarrow \oplus_p L^2({}_pA)\otimes L^2({}^pA)= E(L^2A\otimes L^2A).\] Then we can construct a map \[\Delta: M\rightarrow M\itimes M,\quad x\rightarrow V(x\otimes 1)V^*.\] By direct computation, we see that $\Delta$ extends the comultiplication map on $A$. It is then immediate to check that $\Delta$ is in fact coassociative (where one may as well consider $\Delta$ as a non-unital map from $M$ to $M\otimes M$).

We aim to show that $(M,\Delta)$ can be fitted into the theory of measured quantum groupoids.



\end{document}