% Remarks:
% Podles sphere can be defined as an algebra in $\Rep(SU_q(2))$. Hence, it should make sense as an algebra under the forgetful functor to SU_q(2)-dynamical. By duality for coideals, the same should hold for passage to SU_q(1,1) in fact...
% link with article `Racah - Wigner quantum 6j Symbols, Ocneanu Cells for AN diagrams and quantum groupoids' by Coquereaux?
% Thanks to Makoto, Piotr (?), Leonid
% Donin, J.(IL-BILN); Mudrov, A.(IL-BILN), Quantum groupoids and dynamical categories. 
% Leonid, cf. talk www.fields.utoronto.ca/programs/scientific/13-14/.../Vainerman.pdf
% Level 2 Hecke algebras Brundan
% Concerning locally unital algebras ask J. Vercruysse on recent work 
% Say construction groupoids from forgetful functors on temperley-Lieb already in Enock-Ostrik remark
% Say partial compact quantum groups are proper locally compact quantum groupoids with a discrete base set. Can this be made precise? Is e.g. every measured quantum groupoid which has commutative discrete base and which is `proper' (finiteness integrals on components) of this type? Also compare with properness Timmermann.
% Mention generalization of Neshveyev
% Uniformize enumerates and itemizes
% Reference to Larson paper on cosemisimplicity
% Van Daele and Khang reference?
% More direct references to Gaby's paper on comodules? 
% Caenepeel paper on Galois theory weak Hopf algebras.
% Ref to Vainerman?

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fixme}
\usepackage{mathrsfs}

\usepackage[a4paper]{geometry}
\usepackage{amssymb, amsthm, amsfonts, amsxtra, amsmath}
\usepackage{latexsym}
\usepackage{mathabx}
\usepackage{enumitem}
\usepackage[all]{xy}
\usepackage{graphics}
\usepackage{pdfpages}
\usepackage{epic}
\usepackage{fouridx}
\usepackage{parskip} % paragraphs have no indents and vertical spacings inbetween
\usepackage{bbm}

\makeatletter % need this to avoid the conflict between amsthm and parskip
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother

\DeclareMathOperator{\adj}{\mathrm{adj}}
\DeclareMathOperator{\can}{\mathrm{can}}
\DeclareMathOperator{\Char}{\mathrm{Char}}
\DeclareMathOperator{\dyn}{\mathrm{dyn}}
\DeclareMathOperator{\ext}{\mathrm{e}}
\DeclareMathOperator{\End}{\mathrm{End}}
\DeclareMathOperator{\fin}{\mathrm{f}}
\DeclareMathOperator{\hol}{\mathrm{hol}}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\img}{img}
\DeclareMathOperator{\Ind}{\mathrm{Ind}}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Ker}{\mathrm{Ker}}
\DeclareMathOperator{\Nat}{\mathrm{Nat}}
\DeclareMathOperator{\op}{\mathrm{op}}
\DeclareMathOperator{\Pol}{\mathrm{P}}
\DeclareMathOperator{\Par}{\mathrm{Par}}
\DeclareMathOperator{\Ran}{\mathrm{Ran}}
\DeclareMathOperator{\rcf}{\mathrm{rcfd}}
\DeclareMathOperator{\rd}{\mathrm{d}}
\DeclareMathOperator{\reg}{\mathrm{reg}}
\DeclareMathOperator{\sgn}{\mathrm{sgn}}
\DeclareMathOperator{\Span}{\mathrm{span}}
\DeclareMathOperator{\Spec}{\mathrm{Spec}}
\DeclareMathOperator{\tr}{\mathrm{tr}}
\DeclareMathOperator{\Zz}{\mathrm{Z}}


\newcommand{\dual}[1]{#1^{*}}
\newcommand{\dualop}[1]{#1^{\tr}}
\newcommand{\dualco}[1]{\hat{#1}}
\newcommand{\dualcor}[1]{\check{#1}}
\newcommand{\predual}[1]{{^{\vee}\!#1}}
\newcommand{\co}{\mathrm{co}}
\newcommand{\Corep}{\mathrm{Corep}}
\newcommand{\Corepf}{\mathrm{Corep}^{f}}
\newcommand{\sff}{\textrm{s.f.~}}
\newcommand{\sfs}{\mathrm{sfs}}
\newcommand{\sfd}{\mathrm{sfd}}

\newcommand{\Circt}{{\mathop{\ooalign{$\ovoid$\cr\hidewidth\raise-.05ex\hbox{$\scriptstyle\mathsf T\mkern3.5mu$}\cr}}}} % Woronowicz style tensor product, USUAL SIZE
\newcommand{\Circtv}[1]{\underset{#1}{\mathop{\ooalign{$\ovoid$\cr\hidewidth\raise-.05ex\hbox{$\scriptstyle\mathsf T\mkern3.5mu$}\cr}}}} % Woronowicz style tensor product, USUAL SIZE
\newcommand{\smCirct}{\mathop{\ooalign{$\scriptstyle\ovoid$\cr\hidewidth\raise-.05ex\hbox{$\scriptscriptstyle\mathsf T\mkern2.8mu$}\cr}}}  % Woronowicz style tensor product, SCRIPT SIZE

\newcommand{\nc}{\R}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\h}{\mathfrak{h}}

\newcommand{\kk}{\mathfrak{k}}
\newcommand{\ttt}{\mathfrak{t}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\n}{\mathfrak{n}}
\newcommand{\llll}{\mathfrak{l}}
\newcommand{\uu}{\mathfrak{u}}
\newcommand{\bb}{\mathfrak{b}}
\newcommand{\q}{\mathfrak{q}}
\newcommand{\su}{\mathfrak{su}}
\newcommand{\ssl}{\mathfrak{sl}}
\newcommand{\SSL}{\mathrm{SL}}
\newcommand{\so}{\mathfrak{so}}
\newcommand{\spp}{\mathfrak{sp}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\e}{\mathfrak{e}}
\newcommand{\s}{\mathfrak{s}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\X}{\mathbb{X}}
\newcommand{\Y}{\mathbb{Y}}
\newcommand{\Ss}{\mathbb{S}}
\newcommand{\ZZ}{\mathscr{Z}}
\newcommand{\ad}{\mathrm{ad}}
\newcommand{\Hsp}{\mathcal{H}}
\newcommand{\qn}[2]{\lbrack #1 \rbrack_{#2}}
\newcommand{\fqn}[2]{\lbrack #1 \rbrack_{#2}!}
\newcommand{\bqn}[3]{\left\lbrack \begin{array}{c} \!#1\! \\ \!#2\! \end{array}\right\rbrack_{#3}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\RR}{\mathcal{R}}
\newcommand{\res}{\mathrm{res}}
\newcommand{\cop}{\mathrm{cop}}
\newcommand{\opp}{\mathrm{op}}
\newcommand{\coop}{\mathrm{coop}}
\newcommand{\Rm}{\mathcal{R}}
\newcommand{\wt}{\mathrm{wt}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\CatC}{\mathcal{C}}
\newcommand{\CatD}{\mathcal{D}}
\newcommand{\CatCC}{\mathscr{C}}
\newcommand{\CatDD}{\mathscr{D}}
\newcommand{\Corr}{\mathrm{Corr}}

\newcommand{\Vectf}{\mathrm{Vect}^{f}}
\newcommand{\Vecti}{\mathrm{Vect}^{I^{2}}}
\newcommand{\Vectif}{\mathrm{Vect}_{f}^{I^{2}}}
\newcommand{\Vectrcf}{\mathrm{Vect}_{rcfd}^{I^{2}}}
\newcommand{\Hilb}{\mathrm{Hilb}}
\newcommand{\Hilbf}{\mathrm{Hilb}_{\mathrm{f}}}
\newcommand{\Hilbi}{\mathrm{Hilb}^{I^{2}}}
\newcommand{\Hilbif}{\mathrm{Hilb}^{I^{2}}_{\mathrm{f}}}
\newcommand{\Hilbrcf}{\mathrm{Hilb}^{I^2}_{\mathrm{rcfd}}}

\newcommand{\Star}[2]{{}_{#1}\!*_{#2}}
\newcommand{\vot}{\bar{\otimes}}
\newcommand{\A}{\mathcal{B}}
\newcommand{\Aa}{\mathscr{B}}
\newcommand{\Mor}{\mathrm{Mor}}
\newcommand{\alg}{\mathrm{alg}}
\newcommand{\Gg}{\mathscr{G}}
\newcommand{\ev}{\mathrm{ev}}
\newcommand{\coev}{\mathrm{coev}}
\newcommand{\Rtimes}{\underset{\R}{\times}}
\newcommand{\Rb}{\R^{\bullet}}
\newcommand{\vtimes}{\bar{\otimes}}
\newcommand{\Rr}{\mathscr{R}}
\newcommand{\Tt}{\mathscr{T}}
\newcommand{\Fun}{\mathrm{Fun}}
\newcommand{\Ff}{\Fun_{\fin}}
\newcommand{\itimes}{\underset{I}{\otimes}}
\newcommand{\osum}[1]{\underset{#1}{\sum}^{\oplus}}
\newcommand{\osumc}[1]{\underset{#1}{\sum}^{\bar{\oplus}}}
\newcommand{\oplusc}{\bar{\oplus}}
\newcommand{\wDelta}{\widetilde{\Delta}}
\newcommand{\f}{\mathrm{fin}}
\newcommand{\Rho}{\mathrm{P}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\DA}{\mathcal{A}}
\newcommand{\even}{\mathrm{even}}
\newcommand{\odd}{\mathrm{odd}}
\newcommand{\fd}{\mathrm{fd}}
\newcommand{\Forget}{F}
\newcommand{\Vect}{\mathrm{Vect}}


\newcommand{\GrHA}[3]{#1{\begin{pmatrix} #2,  #3\end{pmatrix}}}% Horizontal grading ordinary style, with argument
\newcommand{\Grs}[3]{#1{\begin{pmatrix} #2,  #3\end{pmatrix}}}

\newcommand{\GrDA}[3]{{}_{\;#2}#1_{#3}} % Horizontal grading bottom style, with argument

\newcommand{\GrVA}[3]{#1{\tiny {\begin{pmatrix} #2\\#3\end{pmatrix}}}} % Vertical grading ordinary style, with argument
\newcommand{\Grt}[3]{#1{\tiny {\begin{pmatrix} #2\\#3\end{pmatrix}}}} 

\newcommand{\GrRA}[3]{#1^{#2}_{#3}} % Vertical grading right style, with argument

\newcommand{\Unit}{\mathbf{1}}
\newcommand{\UnitC}[2]{\Grt{\mathbf{1}}{#1}{#2}} 
\newcommand{\Grru}[2]{{\tiny \begin{pmatrix} #1 \\ #2\end{pmatrix}}}

\newcommand{\eGr}[5]{#1{{\tiny \begin{pmatrix} #2 \quad #3 \\ #4 \quad #5\end{pmatrix}}}}

\newcommand{\pma}[4]{\begin{pmatrix} #1 \quad #2 \\ #3 \quad #4\end{pmatrix}}
\newcommand{\pmat}[4]{{\tiny \begin{pmatrix} #1 \quad #2 \\ #3 \quad #4\end{pmatrix}}}

\newcommand{\UT}[2]{#1{\tiny #2 }}
\newcommand{\Gr}[5]{\fourIdx{#2}{#4}{#3}{#5}{#1}}%TODO: better typesetting
\newcommand{\Grl}[3]{\Gr{#1}{#2}{}{#3}{}}%TODO: better typesetting
\newcommand{\Gru}[3]{\Gr{#1}{}{}{#2}{#3}}
\newcommand{\Grd}[3]{\Gr{#1}{#2}{#3}{}{}}
\newcommand{\gr}[5]{\;{}^{\;#2}_{#4}#1_{#5}^{#3}}%TODO: better typesetting
\newcommand{\eGrr}[3]{#1_{{\tiny \left(#2, #3\right)}}}
\newcommand{\eGrt}[4]{#1{{\tiny \begin{pmatrix} #2 \\ #3 \\ #4 \end{pmatrix}}}}
\newcommand{\Grr}[4]{\begin{pmatrix}#1 \quad #2\\#3&#4\end{pmatrix}}

\newcommand{\Grss}[3]{\UT{#1}{\begin{pmatrix} #2 \; #3\end{pmatrix}}}
\newcommand{\Grb}[7]{\UT{#1}{\begin{pmatrix} #2\quad #3 \\ #4 \quad #5\\ #6 \quad #7\end{pmatrix}}}
\newcommand{\un}[2]{e{{\tiny \begin{pmatrix}#1\\ #2\end{pmatrix}}}}
\newcommand{\unn}[3]{e{{\tiny \begin{pmatrix}#1\\ #2\\#3\end{pmatrix}}}}

\newcommand{\wmult}{\cdot}
\newcommand{\bmult}{*}
\newcommand{\wmate}{\rightarrow}% Change this to source/target notation l(eft) r(ight)
\newcommand{\bmate}{\downarrow}% Change this to source/target notation u(p) d(own)

\newcommand{\aste}[1]{\underset{#1}{\ast}}

\newcommand{\Vv}{\mathcal{V}}

\newcommand{\dT}{\dot T}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lem}[Theorem]{Lemma}
\newtheorem{Prop}[Theorem]{Proposition}
\newtheorem{Cor}[Theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{Def}[Theorem]{Definition}
\newtheorem{Rem}[Theorem]{Remark}
\newtheorem{Exa}[Theorem]{Example}
\newtheorem{Not}[Theorem]{Notation}
\newtheorem{Que}[Theorem]{Question}
\newtheorem{Con}[Theorem]{Conjecture}

%%%%%%%%%%%%%%%%%%%
% Further notation for Section 1
\newcommand{\phic}[2]{\Grt{\phi}{#1}{#2}}

%%%%%%%%%%%%%%%%%%%
% Notation for Section 6
\newcommand{\LGtwo}{L^{2}(\mathscr{G})}
\newcommand{\LGinf}{L^{\infty}(\mathscr{G})}
\newcommand{\CrG}{C^{r}_{0}(\mathscr{G})}
\newcommand{\CuG}{C^{u}_{0}(\mathscr{G})}
\newcommand{\vnDelta}{\overline{\Delta}}
\newcommand{\vnE}{\overline{E}}
\newcommand{\astrl}{\underset{l^{\infty}(I)}{_{\rho}\ast_{\lambda}}}
\newcommand{\otimesrl}{\underset{\nu{}}{_{\rho}\otimes_{\lambda}}}
\newcommand{\vnphi}{\overline{\phi}}
\newcommand{\vnphic}[2]{\Grt{\vnphi}{#1}{#2}}
\newcommand{\vnR}{\overline{R}}
\newcommand{\vntau}{\overline{\tau}}

\date{}


\numberwithin{equation}{section}

\begin{document}
\title{Partial compact quantum groups}

\author{Kenny De Commer\thanks{Department of Mathematics, Vrije Universiteit Brussel, VUB, B-1050 Brussels, Belgium, email: {\tt kenny.de.commer@vub.ac.be}}
\and Thomas Timmermann\thanks{University of M\"{u}nster}}

\maketitle

\begin{abstract}
\noindent Compact quantum groups of face type, as introduced by Hayashi, form a class of quantum groupoids with a classical, finite set of objects. Using the notions of weak multiplier bialgebra and weak multiplier Hopf algebra (resp.~ due to B{\"o}hm--G\'{o}mez-Torrecillas--L\'{o}pez-Centella and Van Daele--Wang), we generalize Hayashi's definition to allow for an infinite set of objects, and call the resulting objects partial compact quantum groups. We prove a Tannaka-Krein-Woronowicz reconstruction result for such partial compact quantum groups using the notion of partial fusion C$^*$-category. As examples, we consider the dynamical quantum $SU(2)$-groups from the point of view of partial compact quantum groups.
 %We also study their connection to the Lesieur--Enock theory of measured quantum groupoids.
\end{abstract}


%\emph{Keywords}:

%AMS 2010 \emph{Mathematics subject classification}:


%17B37: Quantum groups, quantized enveloping algebras
%20G42: quantized function algebras
%46L65: Functional analysis, deformations, quantizations
%81R50: Quantum groups and related algebraic methods
%16T05: Hopf algebras and their applications
%16T10: Bialgebras
%16T15: Coalgebras and comodules; corings
%46L08  $C^*$-modules
%58B32: Geometry of quantum groups


\tableofcontents

\section*{Introduction}

The concept of \emph{face algebra} was introduced by T. Hayashi in \cite{Hay2}, motivated by the theory of solvable lattice models in statistical mechanics. It was further studied in \cite{Hay1,Hay3,Hay4,Hay5,Hay6,Hay7}, where for example associated C$^*$-structures and a canonical Tannaka duality were developed. This canonical Tannaka duality allows one to construct a canonical face algebra from any fusion (C$^*$)-category. For example, a face algebra can be associated to the fusion C$^*$-category of a quantum group at root unity, for which no genuine quantum group implementation can be found. 

In \cite{Nil1,Sch1,Sch2}, it was shown that face algebras are particular kinds of $\times_R$-algebras \cite{Tak2} and of weak bialgebras \cite{Boh3}. More intuitively, they can be considered as quantum groupoids with a classical, finite object set. The wider framework of weak bialgebras allows one to streamline part of the algebraic theory, at the cost perhaps of becoming less intuitive. 

In this article, we want to extend Hayashi's theory by allowing for an \emph{infinite} (but still discrete) object set. This requires passing from weak bialgebras to weak \emph{multiplier} bialgebras \cite{Boh1}. At the same time, our structures admit a piecewise description by what we call a \emph{partial bialgebra}, which is more in the spirit of Hayashi's original definition. In the presence of an antipode, an invariant integral and a compatible $^*$-structure, we call our structures \emph{partial compact quantum groups}. 

The passage to the infinite object case is delicate at points, and requires imposing the proper finiteness conditions on associated structures. However, once all conditions are in place, many of the proofs are similar in spirit to the finite object case. % Rephrase? Don't downplay too much?

Our main result is a Tannaka-Krein-Woronowicz duality result which states that partial compact quantum groups are in one-to-one correspondence with \emph{concrete partial fusion C$^*$-categories}. In its essence, a partial fusion C$^*$-category is a multifusion C$^*$-category \cite{ENO1}, except that we allow an infinite number of irreducible objects as well as an infinite number of summands inside the unit object. By a \emph{concrete} multifusion C$^*$-category, we mean a multifusion C$^*$-category realized inside a category of (locally finite dimensional) bigraded Hilbert spaces. 

% Refs to other TK results, as well as surveys: Tannaka, Krein, Hayashi, Hai, German guy, Szlachanyi, Schauenburg, Woronowicz, Neshveyev-Tuset, Joyal-Street

As an application, we generalize Hayashi's Tannaka duality by showing that any module C$^*$-category over a multifusion C$^*$-category has an associated canonical partial compact quantum group. By the results of \cite{DCY1}, such data can be produced from ergodic actions of compact quantum groups. In particular,  we will consider the particular case of ergodic actions of $SU_q(2)$ for $q$ a non-zero real. This will allow us to show that the construction of \cite{Hay4} generalizes to produce partial compact quantum group versions of the dynamical quantum $SU(2)$-groups of \cite{EtV1,KoR1}, see also \cite{EtN1}, and will provide another viewpoint on the main result of \cite{Sto1}. This construction will immediately provide the right setting for the operator algebraic versions of these dynamical quantum $SU(2)$-groups, which will be studied in the follow-up article \cite{DCT2}.

The precise layout of the paper is as follows.

The first two sections introduce the basic theory of the structures which we will be concerned with in this paper. In the \emph{first section}, we introduce the notions of \emph{partial bialgebra}, \emph{partial Hopf algebra} and \emph{partial compact quantum group}, and show how they are related to the notion of weak multiplier bialgebra \cite{Boh1} and weak multiplier Hopf algebra \cite{VDW1,VDW2}. In the \emph{second section}, we introduce the corresponding notions of \emph{partial tensor category} and \emph{partial fusion C$^*$-category}. 

In the third and fourth section, our main result is proven, namely the Tannaka-Krein-Woronowicz duality. In the \emph{third section} we develop the corepresentation theory of partial Hopf algebras and the representation theory of partial compact quantum groups, and we show that the latter allows one to construct a concrete partial fusion C$^*$-category. In the \emph{fourth} section, we show conversely how any concrete partial fusion C$^*$-category allows one to construct a partial compact quantum group, and we briefly show how the two constructions are inverses of each other.

In the \emph{fifth and sixth section}, we provide some examples of our structures and applications of our main result. In the \emph{fifth section}, we first consider the construction of a canonical partial compact quantum group from any module C$^*$-category for a partial fusion C$^*$-category. As a second application, we introduce the notions of \emph{Morita}, \emph{co-Morita} and \emph{weak Morita equivalence} \cite{Mug1} of partial compact quantum groups, and show that two partial compact quantum groups are weakly Morita equivalent if and only if they can be connected by a string of Morita and co-Morita equivalences. In the \emph{sixth section}, we study in more detail a concrete example of a canonical partial compact quantum group, constructed from an ergodic action of quantum $SU(2)$. In particular, we obtain a partial compact quantum group version of the dynamical quantum $SU(2)$-group. 

%In the final \emph{sixth section}, we show that our partial compact quantum groups have C$^*$-algebraic and von Neumann algebraic completions, and we relate our theory to Lesieur and Enock's theory of measured quantum groupoids \cite{Les1,Eno2,Eno3,Eno4}. 

\emph{Note}: we follow the physicist's convention that inner products on Hilbert spaces are anti-linear in their \emph{first} argument. 



\input{1-partial-algebras.tex}
\input{2-partial-categories.tex}
\input{3-corepresentations.tex}
\input{4-tannaka-krein.tex}
\input{5-examples.tex}
\input{7-free.tex}
%\input{6-op-alg.tex}


\bibliographystyle{habbrv}
%\bibliographystyle{hplain}
%\bibliographystyle{kp}
\bibliography{references}

\end{document}